Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-31 Robustness-Methods-and-Results.tex
robustness re-render with descr

In a final step, we checked whether during the interaction the core
situational need remains a meaningful predictor even when taking other
fundamental psychological needs into account. We again take a two-step
approach, starting with cross-study global three-level test and then
assessing the effects within the individual studies. Within the overall
model we find that across the studies core need fulfillment remained a
strong predictor of outgroup attitudes, even after controlling for the
three self-determination theory need (random slopes model, grand-mean
standardized to account for all levels of variance; \textit{b} = 1.88,
\textit{t}(2.705) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
2.66{]}). Within this overall analysis, none of the self-determination
theory needs independently predicted outgroup attitudes to a
statistically significant extent (all \textit{p} \textgreater{} 0.095).
However, some of the effect sizes were largely comparable to that of the
core need fulfillment (all \textbar{}\textit{b}\textbar{} \textless{}
2.10, particularly that of relatedness fulfillment; see
\tblref{tab:robustnessTblLong} for full results).

When looking at the individual studies, we again saw that core need
fulfillment remained a consistent predictor of outgroup attitudes, even
after accounting for the self-determination theory need (all
\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
\textless{} 0.033). However, across all three studies the fulfillment of
relatedness motives also emerged as a consistent predictor of outgroup
attitudes (all \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all
\textit{p} \textless{} 0.001). Additionally, in the larger studies 2 and
3 competence fulfillment was also related to more positive outgroup
attitudes (study 2: \textit{b} = 0.05, \textit{t}(841.8) = 2.43,
\textit{p} = 0.015, \textit{95\%CI}{[} 0.01, 0.10{]}, study 3:
\textit{b} = 0.06, \textit{t}(30.20) = 2.62, \textit{p} = 0.013,
\textit{95\%CI}{[} 0.01, 0.10{]}). None of the autonomy fulfillment
effects reached statistical significance nor did the competence
fulfillment during study 1 (see \tblref{tab:robustnessTblLong} for the
full results). In short, find that across our samples, relatedness
fulfillment (and to a smaller extend competence fulfillment) are
instrumental in understanding when an outgroup contact leads to more
positive outgroup attitudes. Importantly, even when considering these
effects situational core need fulfillment remains a strong and
consistent predictor of outgroup attitudes. In some cases, we even find
that core need fulfillment takes on some of the variance that would
otherwise be explained by the self-determination theory needs (see
Online Supplemental Material A).

>>>>

In a final step, we checked whether during the interaction the core
situational need remains a meaningful predictor even when taking other
fundamental psychological needs into account. We again take a two-step
approach, starting with cross-study global three-level test and then
assessing the effects within the individual studies. Within the overall
model we find that across the studies core need fulfillment remained a
strong predictor of outgroup attitudes, even after controlling for the
three self-determination theory need (random slopes model, grand-mean
standardized to account for all levels of variance; \textit{b} = 1.88,
\textit{t}(2.702) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
2.66{]}). Within this overall analysis, none of the self-determination
theory needs independently predicted outgroup attitudes to a
statistically significant extent (all \textit{p} \textgreater{} 0.093).
However, some of the effect sizes were largely comparable to that of the
core need fulfillment (all \textbar{}\textit{b}\textbar{} \textless{}
2.10, particularly that of relatedness fulfillment; see
\tblref{tab:robustnessTblLong} for full results).

When looking at the individual studies, we again saw that core need
fulfillment remained a consistent predictor of outgroup attitudes, even
after accounting for the self-determination theory need (all
\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
\textless{} 0.030). However, across all three studies the fulfillment of
relatedness motives also emerged as a consistent predictor of outgroup
attitudes (all \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all
\textit{p} \textless{} 0.001). Additionally, in the larger studies 2 and
3 competence fulfillment was also related to more positive outgroup
attitudes (study 2: \textit{b} = 0.05, \textit{t}(841.8) = 2.43,
\textit{p} = 0.015, \textit{95\%CI}{[} 0.01, 0.10{]}, study 3:
\textit{b} = 0.06, \textit{t}(30.20) = 2.62, \textit{p} = 0.013,
\textit{95\%CI}{[} 0.01, 0.10{]}). None of the autonomy fulfillment
effects reached statistical significance nor did the competence
fulfillment during study 1 (see \tblref{tab:robustnessTblLong} for the
full results). In short, find that across our samples, relatedness
fulfillment (and to a smaller extend competence fulfillment) are
instrumental in understanding when an outgroup contact leads to more
positive outgroup attitudes. Importantly, even when considering these
effects situational core need fulfillment remains a strong and
consistent predictor of outgroup attitudes. In some cases, we even find
that core need fulfillment takes on some of the variance that would
otherwise be explained by the self-determination theory needs (see
Online Supplemental Material A).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{vars\_full }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
  \StringTok{"Core Need"} \OtherTok{=} \StringTok{"CoreNeed"}\NormalTok{,}
  \StringTok{"Competence"} \OtherTok{=} \StringTok{"Competence"}\NormalTok{,}
  \StringTok{"Autonomy"} \OtherTok{=} \StringTok{"Autonomy"}\NormalTok{,}
  \StringTok{"Relatednesss"} \OtherTok{=} \StringTok{"Relatednesss"}\NormalTok{,}
  \StringTok{"Outgroup Interaction"} \OtherTok{=} \StringTok{"OutgroupInteraction"}\NormalTok{,}
  \StringTok{"Accidental"} \OtherTok{=} \StringTok{"InteractionAccidental"}\NormalTok{,}
  \StringTok{"Quality"} \OtherTok{=} \StringTok{"Quality"}\NormalTok{,}
  \StringTok{"Attitudes NL"} \OtherTok{=} \StringTok{"Attitude"}
\NormalTok{)}

\NormalTok{dt\_exp\_all }\OtherTok{\textless{}{-}}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{OutgroupInteraction =}\NormalTok{ (OutgroupInteraction}\FloatTok{{-}1.5}\NormalTok{)}
\NormalTok{  )}

\NormalTok{s1\_MlCor\_full }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{1}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{setdiff}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(vars\_full), }\FunctionTok{c}\NormalTok{(}\StringTok{"InteractionAccidental"}\NormalTok{, }\StringTok{"Quality"}\NormalTok{)),}
    \AttributeTok{labels =} \FunctionTok{setdiff}\NormalTok{(}\FunctionTok{names}\NormalTok{(vars\_full), }\FunctionTok{c}\NormalTok{(}\StringTok{"Accidental"}\NormalTok{, }\StringTok{"Quality"}\NormalTok{))}
\NormalTok{  ) }
\NormalTok{s2\_MlCor\_full }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{2}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
\NormalTok{  ) }
\NormalTok{s3\_MlCor\_full }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{3}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
\NormalTok{  ) }
\NormalTok{all\_MlCor\_full }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_exp\_all,}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
\NormalTok{  ) }

\FunctionTok{rbind}\NormalTok{(}
\NormalTok{  s1\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{add\_column}\NormalTok{(}\AttributeTok{Accidental =} \StringTok{""}\NormalTok{,}
               \AttributeTok{.before =} \StringTok{"Attitudes NL"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{add\_column}\NormalTok{(}\AttributeTok{Quality =} \StringTok{""}\NormalTok{,}
               \AttributeTok{.before =} \StringTok{"Attitudes NL"}\NormalTok{),}
\NormalTok{  s2\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
\NormalTok{  s3\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
\NormalTok{  all\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{)}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kbl}\NormalTok{(.,}
      \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
      \AttributeTok{caption =} \StringTok{"Full Sample: Correlation Table and Descriptive Statistics"}\NormalTok{,}
      \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
      \AttributeTok{align =} \FunctionTok{c}\NormalTok{(}\StringTok{"l"}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)))  }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_classic}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_header\_above}\NormalTok{(}
\NormalTok{    .,}
    \FunctionTok{c}\NormalTok{(}
      \StringTok{""}\NormalTok{,}
      \StringTok{"Correlations"} \OtherTok{=} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full),}
      \StringTok{"Descriptives"} \OtherTok{=} \FunctionTok{nrow}\NormalTok{(s3\_MlCor\_full) }\SpecialCharTok{{-}} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full)}
\NormalTok{    )}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 2"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,}
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 3"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Across Studies"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(all\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{footnote}\NormalTok{(}
    \AttributeTok{general =} \FunctionTok{c}\NormalTok{(}
      \StringTok{"Upper triangle: Between{-}person correlations;"}\NormalTok{,}
      \StringTok{"Lower triangle: Within{-}person correlations;"}\NormalTok{,}
      \StringTok{"*** p \textless{} .001, ** p \textless{} .01,  * p \textless{} .05"}\NormalTok{,}
      \StringTok{"Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."}
\NormalTok{    )}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \StringTok{"scale\_down"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{begin\{minipage\}[t][}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textheight][t]\{}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textwidth\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{minipage\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{save\_kable}\NormalTok{(}\StringTok{"Tables/descrFullWideAppB.tex"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{vars\_out }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
  \StringTok{"Core Need"} \OtherTok{=} \StringTok{"CoreNeed"}\NormalTok{,}
  \StringTok{"Competence"} \OtherTok{=} \StringTok{"Competence"}\NormalTok{,}
  \StringTok{"Autonomy"} \OtherTok{=} \StringTok{"Autonomy"}\NormalTok{,}
  \StringTok{"Relatednesss"} \OtherTok{=} \StringTok{"Relatednesss"}\NormalTok{,}
  \StringTok{"Practical Need"} \OtherTok{=} \StringTok{"practical\_need\_dum"}\NormalTok{,}
  \StringTok{"Psychological Need"} \OtherTok{=} \StringTok{"psychological\_need\_dum"}\NormalTok{,}
  \StringTok{"Accidental"} \OtherTok{=} \StringTok{"InteractionAccidental"}\NormalTok{,}
  \StringTok{"Quality"} \OtherTok{=} \StringTok{"Quality"}\NormalTok{,}
  \StringTok{"Attitudes NL"} \OtherTok{=} \StringTok{"Attitude"}
\NormalTok{)}

\NormalTok{s1\_MlCor\_out }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{1}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
\NormalTok{  ) }
\NormalTok{s2\_MlCor\_out }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{2}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
\NormalTok{  ) }
\NormalTok{s3\_MlCor\_out }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{3}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
\NormalTok{  ) }
\NormalTok{all\_MlCor\_out }\OtherTok{\textless{}{-}} 
  \FunctionTok{MlCorMat}\NormalTok{(}
    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
\NormalTok{  ) }

\FunctionTok{rbind}\NormalTok{(}
\NormalTok{  s1\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
\NormalTok{  s2\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
\NormalTok{  s3\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
\NormalTok{  all\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{)}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kbl}\NormalTok{(.,}
      \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
      \AttributeTok{caption =} \StringTok{"Outgroup Interaction Sample: Correlation Table and Descriptive Statistics"}\NormalTok{,}
      \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
      \AttributeTok{align =} \FunctionTok{c}\NormalTok{(}\StringTok{"l"}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)))  }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_classic}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_header\_above}\NormalTok{(}
\NormalTok{    .,}
    \FunctionTok{c}\NormalTok{(}
      \StringTok{""}\NormalTok{,}
      \StringTok{"Correlations"} \OtherTok{=} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out),}
      \StringTok{"Descriptives"} \OtherTok{=} \FunctionTok{nrow}\NormalTok{(s3\_MlCor\_out) }\SpecialCharTok{{-}} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out)}
\NormalTok{    )}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 2"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,}
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 3"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Across Studies"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(all\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{footnote}\NormalTok{(}
    \AttributeTok{general =} \FunctionTok{c}\NormalTok{(}
      \StringTok{"Upper triangle: Between{-}person correlations;"}\NormalTok{,}
      \StringTok{"Lower triangle: Within{-}person correlations;"}\NormalTok{,}
      \StringTok{"*** p \textless{} .001, ** p \textless{} .01,  * p \textless{} .05"}
\NormalTok{    )}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \StringTok{"scale\_down"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{begin\{minipage\}[t][}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textheight][t]\{}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textwidth\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{minipage\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
  \FunctionTok{save\_kable}\NormalTok{(}\StringTok{"Tables/descrOutWideAppB.tex"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
